### 2021-10-11 docs/paper/sections/6_conclusion.tex
Fix consecutive footnotes manually

We believe that our tool has further potential to support package developers in surveying downstream dependencies and thus have assembled a shortlist of open to-dos for the project.
Among others, we want to expand the applicability of the tool by adding support for further ecosystems and programming languages.
The user experience of the tool could be improved by increasing the liveness of displayed data, for instance, by automatically reflecting source code changes.
For better performance, usage samples could be cached, and finer-grained UI updates could be implemented.
Last but not least, we want to improve the integration of the extension by adding support for browser environments such as github.dev\footnote{\url{https://code.visualstudio.com/api/extension-guides/web-extensions}}\footnote{\url{https://docs.github.com/en/codespaces/the-githubdev-web-based-editor}} and by connecting it to the GitHub Remote Repositories extension\footnote{\url{https://marketplace.visualstudio.com/items?itemName=GitHub.remotehub}}.

>>>>

We believe that our tool has further potential to support package developers in surveying downstream dependencies and thus have assembled a shortlist of open to-dos for the project.
Among others, we want to expand the applicability of the tool by adding support for further ecosystems and programming languages.
The user experience of the tool could be improved by increasing the liveness of displayed data, for instance, by automatically reflecting source code changes.
For better performance, usage samples could be cached, and finer-grained UI updates could be implemented.
Last but not least, we want to improve the integration of the extension by adding support for browser environments such as github.dev\footnote{\url{https://code.visualstudio.com/api/extension-guides/web-extensions}}\footnoteseparator\footnote{\url{https://docs.github.com/en/codespaces/the-githubdev-web-based-editor}} and by connecting it to the GitHub Remote Repositories extension\footnote{\url{https://marketplace.visualstudio.com/items?itemName=GitHub.remotehub}}.
